\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-10-30 Latex/paper.tex
# typo in ois convexity

\subsection{OIS futures}
In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
\begin{align*}
R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
\end{align*}
We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}^{t_1}$ that will observable during whole period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales  
\begin{align*} 
\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}
We must do several obeservations. The first observation is that
\begin{align*}
F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
\end{align*}
The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
\end{equation}
The second observation, is that under the dyam we must do is that
\begin{equation}\label{R_ois_avg}
\mathbb{E}_{t}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}_t^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
\end{equation}
In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
\begin{equation*}
I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
\end{equation*}
then for $t < t_0$ from (\ref{clark-okone}) and (\ref{approximation_D_s_x_t}), we have the next representation for $I(t_0,t_1)$
\begin{align}\label{apprx_I_t0_t1}
I(t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
&\approx \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\hat{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
&= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1} g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
\end{align}
Therefore, we can get the next approximation
\begin{align*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}^{t_1}}\left(R(t_0,t_1)\right) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( \exp(I(t_0,t_1)) \right)\\
&= \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\exp\left(\int_{0}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
\end{align*}
where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. Now, from the Girsanov's theorem we get that
\begin{equation*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
\end{equation*}
Therefore we have that

@@

We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow
\begin{align}\label{cms_expedted_value}
P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{align}
where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. In order to reduce the complexity to explain the movement od the forward curve, it is a common pratice to asumme that
\begin{equation*}
M(t) = f(S^{ois}_{a,b}(t))
\end{equation*}
where $f(\cdot)$ is known as mapping function. There is a extensive literature how to define this function (see Piterbarg Volume III), in later we will see some particular examples. Under the last assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
\begin{align*}
f(S^{ois}_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S^{ois}_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S^{ois}_{a,b}(T_a)) \right) dW^{01(a,b)}_{s} \\
&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
\end{align*}
Therefore, we can define the convexity adjustment for a CMS the next way
\begin{align*}
CA_{CMS}(T_a,T_b) = \\
01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right)
\end{align*}
Now if we use again the Clark-Ocone representation, but in this case for $S_{a,b}(T_a)$, we can do the next approximation
\begin{align*}
CA_{CMS}(T_a,T_b) &\approx 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left( S^{ois}_{a,b}(T_a) - S^{ois}_{a,b}(0)\right)\right) \\
&= 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) -  S_{a,b}(0) S^{ois}_{a,b}(0)\right)
\end{align*}
Where we have used that $S_{a,b}(t)$ and $S^{ois}_{a,b}(T_a)$ are $01(a,b)$-martingale. Also, if we use Itô formula we get that
\begin{align*}
dS^{ois}_{a,b}(t,x_t,y_t) &= \partial_{x}S^{ois}_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)}  \\
dS_{a,b}(t,x_t,y_t) &= \partial_{x}S_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)} 
\end{align*}
with initial condition respectivaly $S^{ois}_{a,b}(0)$ and $S_{a,b}(0)$. Then we have that
\begin{align*}
\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) \right) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(\int_0^{T_a} \partial_{x}S_{a,b}(u,x_u,y_u) \partial_{x}S^{ois}_{a,b}(u,x_u,y_u)  \eta^{2}(u,x_u,y_u)
du \right)  + S_{a,b}(0) S^{ois}_{a,b}(0) \\
&\approx  \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0)\int_0^{T_a} \eta^{2}(u,x_0,\hat{y}_u) + S_{a,b}(0) S^{ois}_{a,b}(0).
du
\end{align*}
Therefore, if se use the last equality we can approximate $CA_{CMS}(T_a,T_b)$ the next way

@@

\begin{example}
In ghe case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
$$
\eta(t,x_t, y_t) = \sigma\exp(-kt)
$$
\end{example}
Therefore (\ref{cms_adjustment}) is reduced to
\begin{equation}\label{hullwhite_cms_convexity}
01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \partial_{x}S_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
\end{equation}
A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model). We must to impose two equations in order to get $\alpha$ and $\beta$. The first equation follows straightforward from the definition of $M(t,T_p)$. Since, $M(t,T_p)$ is a $01(a,b)-$martingale we must have that
\begin{equation*}
\mathbb{E}^{01(a,b)}\left(\alpha S^{ois}_{a,b}(T_a) + \beta \right) = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b)}.
\end{equation*}
Therefore
\begin{equation*}
\beta = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
\end{equation*}
Under a separable HJM dynamic we must have that
\begin{equation*}
\alpha \partial_{x} S^{ois}_{a,b}(0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right).
\end{equation*}
Then
\begin{equation*}
\alpha = -\frac{M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right)}{\partial_{x} S^{ois}_{a,b}(0)}.
\end{equation*}
Then from the last equalities, we can approximate the convexity adjustment of a CMS rate as
\begin{align*}
CA_{CMS}(T_a,T_b) \\ 
\approx 01(0,T_a,T_b) \alpha \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
= - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0)  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
\end{align*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method

>>>>

\subsection{OIS futures}
In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
\begin{align*}
R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
\end{align*}
We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}^{t_1}$ that will observable during whole period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales  
\begin{align*} 
\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}
We must do several obeservations. The first observation is that, we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
\end{align*}
The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
\end{equation}
The second observation, is that under the dyam we must do is that
\begin{equation}\label{R_ois_avg}
\mathbb{E}_{t}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}_t^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
\end{equation}
In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
\begin{equation*}
I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
\end{equation*}
then for $t < t_0$ from (\ref{clark-okone}) and (\ref{approximation_D_s_x_t}), we have the next representation for $I(t_0,t_1)$
\begin{align}\label{apprx_I_t0_t1}
I(t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
&\approx \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\hat{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
&= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1} g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
\end{align}
Therefore, we can get the next approximation
\begin{align*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}^{t_1}}\left(R(t_0,t_1)\right) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( \exp(I(t_0,t_1)) \right)\\
&= \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\exp\left(\int_{0}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
\end{align*}
where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. Now, from the Girsanov's theorem we get that
\begin{equation*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
\end{equation*}
Therefore we have that

@@

We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow
\begin{align}\label{cms_expedted_value}
P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{align}
where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. In order to reduce the complexity to explain the movement od the forward curve, it is a common pratice to asumme that
\begin{equation*}
M(t) = f(S^{ois}_{a,b}(t))
\end{equation*}
where $f(\cdot)$ is known as mapping function. There is a extensive literature how to define this function (see Piterbarg Volume III), in later we will see some particular examples for this mapping function. Under the last assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
\begin{align*}
f(S^{ois}_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S^{ois}_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S^{ois}_{a,b}(T_a)) \right) dW^{01(a,b)}_{s} \\
&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
\end{align*}
Therefore, we can define the convexity adjustment for a CMS the next way
\begin{align*}
&CA_{CMS}(T_a,T_b)  \\
=&01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right)
\end{align*}
Now if we use again the Clark-Ocone representation, but in this case for $S_{a,b}(T_a)$ we get that
\begin{align*}
CA_{CMS}(T_a,T_b) &\approx 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left( S^{ois}_{a,b}(T_a) - S^{ois}_{a,b}(0)\right)\right) \\
&= 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) -  S_{a,b}(0) S^{ois}_{a,b}(0)\right)
\end{align*}
Where we have used that $S_{a,b}(t)$ and $S^{ois}_{a,b}(T_a)$ are $01(a,b)$-martingale. Now, if we use Itô formula to $S^{ois}_{a,b}(t)$ and $S_{a,b}(t)$ we have that
\begin{align*}
dS^{ois}_{a,b}(t,x_t,y_t) &= \partial_{x}S^{ois}_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)}  \\
dS_{a,b}(t,x_t,y_t) &= \partial_{x}S_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)} 
\end{align*}
with initial condition $S^{ois}_{a,b}(0)$ and $S_{a,b}(0)$ respectivaly. Then 
\begin{align*}
\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) \right) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(\int_0^{T_a} \partial_{x}S_{a,b}(u,x_u,y_u) \partial_{x}S^{ois}_{a,b}(u,x_u,y_u)  \eta^{2}(u,x_u,y_u)
du \right)  + S_{a,b}(0) S^{ois}_{a,b}(0) \\
&\approx  \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0)\int_0^{T_a} \eta^{2}(u,x_0,\hat{y}_u) + S_{a,b}(0) S^{ois}_{a,b}(0).
du
\end{align*}
Therefore, from the last equality we can approximate $CA_{CMS}(T_a,T_b)$ the next way

@@

\begin{example}
In ghe case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
$$
\eta(t,x_t, y_t) = \sigma\exp(-kt)
$$
\end{example}
Therefore (\ref{cms_adjustment}) is reduced to
\begin{equation}\label{hullwhite_cms_convexity}
01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \partial_{x}S_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
\end{equation}
A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model). We must to impose two equations in order to get $\alpha$ and $\beta$. The first equation follows straightforward from the definition of $M(t,T_p)$. Since, $M(t,T_p)$ is a $01(a,b)-$martingale we must have that
\begin{equation*}
\mathbb{E}^{01(a,b)}\left(\alpha S^{ois}_{a,b}(T_a) + \beta \right) = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b)}.
\end{equation*}
Therefore
\begin{equation*}
\beta = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
\end{equation*}
Under a separable HJM dynamic we must have that
\begin{equation*}
\alpha \partial_{x} S^{ois}_{a,b}(0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right).
\end{equation*}
Then
\begin{equation*}
\alpha = -\frac{M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right)}{\partial_{x} S^{ois}_{a,b}(0)}.
\end{equation*}
Then from the last equalities, we can approximate the convexity adjustment of a CMS rate as
\begin{align*}
&CA_{CMS}(T_a,T_b) \\ 
\approx& 01(0,T_a,T_b) \alpha \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
=& - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0)  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
\end{align*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method
